Neuro IV

### 2017-08-24 neuro4.rmd
Added short cases, should try to start new sentence on new line from now on

@@

>>>>

One eye: probably not occipital lobe as at optic chiasm, left optic tract gets info from both eyes (left visual field), sim for right.

Questions to ask:

-  Fam Hx
-  What was she doing at the time?
-  Any headaches when she does move her eye?
-  Associated symptoms: numbness, tingling, incontinence?
-  Nature of pain
-  Better or worse
-  Onset: there all day?
-  Allergies, drugs

Ex for pupilliary reflex

-  Direct
-  Consensual

Optic neuritis: inflammed myelin sheaths of optic nerve.
85% of cases permanent damage to optic nerve.
Tx: steroids for severe or chronic cases.

Causes of demyelinating disease: autoimmune, Vit B12,

Dx for MS: McDonald criteria: 2 diff lesions in 2 diff places and 2 diff times

@@

Peripheral nerves is site.

Breathless: up to 30% of GBS require ventilation.

Main cause is campylobacter causing GIT infns. 
Bacteria have LPS which are similar to myelin gangliocytes => creating molecular mimicry. 
Early lymphocytic infiltrates than macrophage mediated stripping of myelin. 
Segmental demyelination then infiltrates. 
Most repair normally.

| Mnemonic    | UMN                                 | LMN           |
|-------------|-------------------------------------|---------------|
| Strength    | $\Downarrow$                        | $\Downarrow$  |
| Tone        | $\Uparrow$                          | $\Downarrow$  |
| Others      | Superficial reflexes. Absent clonus | Fasiculations |
| Reflexes    | $\Uparrow$                          | $\Downarrow$  |
| Muscle mass | $\sim N$                            | $\Downarrow$  |
| Babinski    | $(+)$                               | $(-)$         |

Mx:

-  Plasmaphoresis or Ig but NOT both
-  20% mortality if ventilated
-  Long term complications DVT, paralysis, death, peripheral neuropathy
-  Recovery takes a *long* time: 6/12 to *years*
